Supermartingales and Termination Analysis of Statistical PCF

### 2021-01-10 LICS21/related.tex
Sec. 1: Added outline, "additional materials in appendices". Tidying things up, saving space.
Reformatted def. of sparse ranking function (and two other similar def.), making it more compact.

% !TEX root = main.tex
\section{Related work, conclusion and further directions}
\label{sec:related}
We have not yet been able to prove our conjecture that every term is antitone rankable if all of the terms reachable from it are AST, which would imply that \Cref{thm:antitone rankable implies termination} is almost complete.

The definition \label{def:more general red} of redexes and which positions are acceptable to reduce at is sufficiently restrictive to guarantee Church-Rosserness, but is also a little more restrictive in some cases than is necessary for this purpose. For example, if the argument of a function is not yet a value, but its reduction to a value would be deterministic, or the function is affine, then applying the function before reducing its argument would not cause any problematic duplication of random samples. Similarly, if $\tsample$ occurs at position $\alpha;@_2;\beta;\lambda;\gamma$, but the function at $\alpha;@_1$ is affine, evaluatinf the $\tsample$ may in some cases also work fine. A more complete characterisation of which redexes can be reduced without breaking Church-Rosserness could be interesting.

>>>>

% !TEX root = main.tex
\section{Related work and further directions}

\lo{TODO. Related work (.75 column). Discuss \cite{DBLP:conf/birthday/BlancLM05}.}

\lo{Our results specialise to proving termination of non-random lambda calculus, which is much studied. Our approach is closest in spirit to Jones' work on size-change argument. Dal Lago's work builds on this. We think that martingales are a good framework for generalising / unifying with size-change work.}

\lo{Other approaches, mainly based on types, are complementary to ours.}

\lo{Kobayashi et al.: PHORS are strictly weaker in expressivity.}

\label{sec:related}
We have not yet been able to prove our conjecture that every term is antitone rankable if all of the terms reachable from it are AST, which would imply that \Cref{thm:antitone rankable implies termination} is almost complete.

The \Cref{def:more general red} of redexes and which positions are acceptable to reduce at is sufficiently restrictive to guarantee Church-Rosserness, but is also a little more restrictive in some cases than is necessary for this purpose. For example, if the argument of a function is not yet a value, but its reduction to a value would be deterministic, or the function is affine, then applying the function before reducing its argument would not cause any problematic duplication of random samples. Similarly, if $\tsample$ occurs at position $\alpha;@_2;\beta;\lambda;\gamma$, but the function at $\alpha;@_1$ is affine, evaluatinf the $\tsample$ may in some cases also work fine. A more complete characterisation of which redexes can be reduced without breaking Church-Rosserness could be interesting.
